---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# oaqc

<!-- badges: start -->
<!-- badges: end -->

This package provides an efficient algorithm to calculate 
for a given graph the **o**rbit-**a**ware **q**uad **c**ensus. 
More precisely the frequency distribution of all induced and 
non-induced non-isomorphic four node subgraphs, 
i.e. <i>quads</i>, on a node and edge level; see the figure 
below for the relation between orbit and quad.

![quad census](vignettes/quad_census.svg)

## Installation

You can install the development version of oaqc like so:

``` r
remotes::install_github("schochastics/oaqc")
```
## Input

The input can either be an edgelist (matrix or data.frame) or a graph Object ('igraph')

Despite the input format the graph should not contain loops 
or multi-edges and the vertex indices have to lie in range 
[0,n-1) with n denoting the number of vertices in the graph. 
Note that if the smallest index is 1 the algorithm will create
an isolated vertex with index 0.

## Calculating the orbit-aware quad census

The following code exemplifies the use of this package.

```{r}
library(oaqc)
### k4, pure R
k4 <- data.frame(
    source = c(0, 0, 0, 1, 1, 2),
    target = c(1, 2, 3, 2, 3, 3)
)
k4orbits <- oaqc(k4, non_ind_freq = FALSE, file = "")
k4orbits
```
In order to calculate the non-induced frequencies as well 
just set the corresponding flag to `TRUE`.

Since the orbit-aware frequencies can be rather large integers, 
which can cause some problems with R, the results can be 
directly written to a file.

## Result

The results of the, e.g., induced frequencies of the nodes 
in orbit 10 can be accessed in the following way.

```{r}
k4orbits$n_orbits_ind[, 10]
```